Making Sequential Programs Deterministic

### 2019-03-19 paper.tex
bib file
design sketch
Add macros, change title
Use more bibliographies
Add todo fork keywords

@@

%% Title information
\title{Compile Time Verification of Deterministic properties for Sequential Programs}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Subtitle}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
Text of abstract \ldots.
\end{abstract}

@@

%% Keywords
%% comma separated list
\keywords{keyword1, keyword2, keyword3}  %% \keywords are mandatory in final camera-ready submission

@@

\section{Introduction}

Text of paper \ldots

@@

%% Bibliography
%\bibliography{bibfile}

%% Appendix
\appendix
\section{Appendix}

Text of appendix \ldots

>>>>

\usepackage{url}

\usepackage{color}
%% Comment out one of these two definitions.
% \newcommand{\todo}[1]{\relax}
\newcommand{\todo}[1]{{\color{red}\bfseries [[#1]]}}

% \|name| or \mathid{name} denotes identifiers and slots in formulas
\def\|#1|{\mathid{#1}}
\newcommand{\mathid}[1]{\ensuremath{\mathit{#1}}}
% \<name> or \codeid{name} denotes computer code identifiers
\def\<#1>{\codeid{#1}}
\protected\def\codeid#1{\ifmmode{\mbox{\sf{#1}}}\else{\sf #1}\fi}
\protected\def\codeid#1{\ifmmode{\mbox{\ttfamily{#1}}}\else{\ttfamily #1}\fi}
\protected\def\codeid#1{\ifmmode{\mbox{\smaller\ttfamily{#1}}}\else{\smaller\ttfamily #1}\fi}

@@

%% Title information
% \title{Compile Time Verification of Deterministic properties for Sequential Programs}
\title{Making Sequential Programs Deterministic}
         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Subtitle}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
\todo{Text of abstract \ldots.}
\end{abstract}

@@

%% Keywords
%% comma separated list
\keywords{\todo{keyword1}, \todo{keyword2}, \todo{keyword3}}  %% \keywords are mandatory in final camera-ready submission

@@

\input{introduction.tex}
\input{design.tex}

@@

%% Bibliography
%\bibliographystyle{ACM-Reference-Format.bst}
\bibliography{paper,bibstring-unabbrev,testing,crossrefs}

%% Appendix
%\appendix
%\section{Appendix}
%
%Text of appendix \ldots
